Fivebranes

### 2022-05-30 fivebranes/kr.tex
merge

In \cite{KacRudakov} an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$.

We first split the coordinates on the formal five-disk as
\[
(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
\]
In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.

Assign the following weights to the super Lie algebra $E(5|10)$. 
\begin{itemize} 
\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
\item the parity of an element carries an additional weight of $-1$. 
Thus, for example, the odd element $[w_1 \d z_1] \in \Pi \Omega^1(\Hat{D}^5)/{\rm Im}(\del)$ carries weight $+1 - 1 = 0$. 
\end{itemize} 
The weight grading is concentrated in degrees $\geq -1$. 
In particular, there is a decomposition of super vector spaces
\beqn\label{eqn:decomp1}
E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
\eeqn
with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$. 
In particular 
\beqn 
\label{eqn:e36iso}
E(3|6) \cong V_0 \subset E(5|10)
\eeqn
is a sub super Lie algebra and each $V_n$ is a module for $E(3|6)$.

@@

We can extend the weight grading of $E(5|10)$ to a weight grading of the central extension $\Hat{E(5|10)}$ by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super vector spaces
\beqn\label{eqn:decomp1}
E(5|10) = \prod_{n \geq -1} V_n
\eeqn
Here $V_{-1}$ is a $\C$-extension of the module $\til V_{-1}$ defined in the decomposition above.
Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.
In particular, we have the following.

@@

The super Lie algebra $E(5|10)$ carries a (non-cohomological) consistent $\Z$-grading by declaring 
\begin{itemize}
\item $\deg z_i = \deg w_a = 2$, so that $\deg \del_{z_i} = \deg \del_{w_a} = -2$. 
\item $\deg \d z_i = \deg \d w_a = -1/2$.
\end{itemize}
This consistent $\Z$-grading extends to the central extension of $E(5|10)$ by declaring that the central term has degree $-5$.

\subsection{Irreducible representations of $E(3|6)$}
Thinking of the super Lie algebra $E(3|6)$ as the weight zero subalgebra of $\Hat{E(5|10)}$ (or even before centrally extending) then it carries an induced consistent $\Z$-grading. 
Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
In particular, as a super vector space
\[
E(3|6) = \oplus_{j \geq -2} \fg_j
\]
where
\begin{itemize}
\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is completely even. 
\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is completely odd. 
\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is completely even. 
Explicitly, the Cartan of $\lie{sl}(3)$ is spanned by 
\[
h_1 = z_1 \del_{z_1} - z_2 \del_{z_2}, \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3} .
\]
The Cartan of $\lie{sl}(2)$ is spanned by
\[
h_3 = w_1 \del_{w_1} - w_2 \del_{w_2} .
\]
The Cartan of $\lie{gl}(1)$ is spanned by
\[
Y = \frac23 \sum_{i=1,2,3} z_i \del_{z_i} - \sum_{a=1,2} w_a \del_{w_a} .
\]
\end{itemize}

@@

We will be interested in Verma modules associated to two particular types of $\fg_0$-modules
\begin{align*}
V_A & = \C[z_i, w_a] \\
V_B & = \C[z_i, \del_{w_a}]_{[2]} .
\end{align*}
Here, the subscript $[2]$ means that we shift $\lie{gl}(1)$ to act by the differential operator 
\[
Y_{[2]} = Y + 2 \id_{V_B} .
\]
For $X = A,B$ we let 
\[
V_X^{m,n} = \{f \in V_X \; | \; \sum z_i \del_{z_i} f = m f , \quad \sum w_a \del_{w_a} f = n f.\} 
\]
so that $V_X = \sum_{m,n} V_X^{m,n}$. 
There is a similar decomposition of the resulting Verma modules $M(V_X)$ in terms of the Verma modules $M(V_{X}^{m,n})$.

An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda$ which we denote by
\begin{align*}
\lambda_i & = \lambda (h_i) \in \Z_{\geq 0}, \\
 y & = \lambda(Y)\in \C . 
\end{align*}
There is an isomorphism of $\fg_0$-modules
\begin{align*}
V_A^{p,r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
V_B^{p,-r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2) .
\end{align*}

@@

Define the (super) character of an $E(3|6)$-module $M$ by the formula
\[
\ch \, M  \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
\]
As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
\[
M(V) = \Sym(\lie{g}_{<0}) \otimes V .
\]
We have $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where we recall that $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.

@@

\subsection{Characters for degenerate modules of type A} \label{s:typeA}

There is a cohomological description of the irreducible modules of type $A$
\[
I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
\]
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\beqn\label{eqn:les1}
0 \leftarrow I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) \leftarrow M(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) \leftarrow M(\lambda_1+1,0,\lambda_3+1;\frac23 \lambda_1 - \lambda_3-\frac13) \leftarrow \cdots .
\eeqn
%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]

\parsec[s:typeAunrefinedKR]
In this section we compute the {\em unrefined} character of the type A modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
From the long exact sequence \eqref{eqn:les1} we have the following expression 
\[
\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} = \sum_{j \geq 0} \ch M(\lambda_1+j,0,\lambda_3+j;\frac23 \lambda_1 - \lambda_3 - \frac{j}{3}) .
\]

@@

There is a cohomological description of the irreducible modules of type $B$ similar to the type A case above.
Let $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
We are only interested in the case $\lambda_1 = 0$.  
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\begin{multline}\label{eqn:les1}
0 \leftarrow  I_B(0,\lambda_3) \leftarrow \\ \leftarrow M(0,0,\lambda_3;\lambda_3 + 2) \leftarrow  M(1,0,\lambda_3-1;\frac{11}{3} - \lambda_3)  \leftarrow \cdots \leftarrow M(\lambda_3, 0, 0;\frac23 \lambda_3 +2) \leftarrow \\
 \leftarrow M(\lambda_3+2, 0, 0; \frac23 \lambda_3 + \frac43) \leftarrow M(\lambda_3+3, 0, 1; \frac23 \lambda_3 + 2) \leftarrow \cdots .
\end{multline}
There are $\lambda_3+1$ terms in the second line above .

>>>>

In \cite{KacRudakov} an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$. 
We first split the coordinates on the formal five-disk as
\[
(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
\]
In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.

\parsec[s:e510weight]
Assign the following weights to the super Lie algebra $E(5|10)$. 
\begin{itemize} 
\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
\item the parity of an element carries an additional weight of $-1$. 
Thus, for example, the odd element $[w_1 \d z_1] \in \Pi \Omega^1(\Hat{D}^5)/{\rm Im}(\del)$ carries weight $+1 - 1 = 0$. 
\end{itemize} 
The weight grading is concentrated in degrees $\geq -1$. 
In particular, there is a decomposition of super vector spaces
\beqn\label{eqn:decomp1}
E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
\eeqn
with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$. 
In particular 
\beqn 
\label{eqn:e36iso}
E(3|6) \cong V_0 \subset E(5|10)
\eeqn
is a sub super Lie algebra and each $V_n$ is a module for $E(3|6)$.

@@

We can extend the weight grading of $E(5|10)$ to a weight grading of the central extension $\Hat{E(5|10)}$ by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super vector spaces
\beqn\label{eqn:decomp1}
\Hat{E(5|10)} = \prod_{n \geq -1} V_n
\eeqn
Here $V_{-1}$ is a $\C$-extension of the module $\til V_{-1}$ defined in the decomposition above.
Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.
In particular, we have the following.

@@

The super Lie algebra $E(5|10)$ carries a (non-cohomological) consistent $\Z$-grading by declaring 
\begin{itemize}
\item $\deg z_i = \deg w_a = 2$, so that $\deg \del_{z_i} = \deg \del_{w_a} = -2$. 
\item $\deg \d z_i = \deg \d w_a = -1/2$.
\end{itemize}
This consistent $\Z$-grading extends to the central extension of $E(5|10)$ by declaring that the central term has degree $-5$. 
Note that this is different from the weight grading we recalled in \S \ref{s:e510weight}.

\subsection{Irreducible representations of $E(3|6)$}
Thinking of the super Lie algebra $E(3|6)$ as the weight zero subalgebra of $\Hat{E(5|10)}$ (or even before centrally extending) then it carries an induced consistent $\Z$-grading. 
Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
In particular, as a super vector space
\[
E(3|6) = \oplus_{j \geq -2} \fg_j
\]
where for small values of $j$ we have:
\begin{itemize}
\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is completely even. 
\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is completely odd. 
\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is completely even. 
Explicitly, the Cartan of $\lie{sl}(3)$ is spanned by 
\[
h_1 = z_1 \del_{z_1} - z_2 \del_{z_2}, \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3} .
\]
The Cartan of $\lie{sl}(2)$ is spanned by
\[
h_3 = w_1 \del_{w_1} - w_2 \del_{w_2} .
\]
The Cartan of $\lie{gl}(1)$ is spanned by
\[
Y = \frac23 \sum_{i=1,2,3} z_i \del_{z_i} - \sum_{a=1,2} w_a \del_{w_a} .
\]
\end{itemize}

@@

We will be interested in Verma modules associated to two particular types of $\fg_0$-modules
\begin{align*}
V_A & = \C[z_i, w_a] \\
V_B & = \C[z_i, \del_{w_a}]_{[2]} .
\end{align*}
Here, the subscript $[2]$ means that we shift $\lie{gl}(1)$ to act by the differential operator 
\[
Y_{[2]} = Y + 2 \id_{V_B} .
\]
For $X = A,B$ we let 
\[
V_X^{m,n} = \{f \in V_X \; | \; \sum z_i \del_{z_i} f = m f , \quad \sum w_a \del_{w_a} f = n f.\} \subset V_X
\]
so that $V_X = \oplus_{m,n} V_X^{m,n}$. 
There is a similar decomposition of the resulting Verma modules $M(V_X)$ in terms of the Verma modules $M(V_{X}^{m,n})$.

An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda$ whose components we denote by
\begin{align*}
\lambda_i & = \lambda (h_i) \in \Z_{\geq 0}, \\
 y & = \lambda(Y)\in \C . 
\end{align*}
There is an isomorphism of $\fg_0$-modules
\begin{align*}
V_A^{p,r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
V_B^{p,-r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2) .
\end{align*} 
Note for type $A,B$ we have $\lambda_2 = 0$. 
To simplify notation we will write 
\begin{align*}
F_A(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
F_B(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2)  
\end{align*}
and similarly $M_A(\lambda_1,\lambda_3)$, $M_B(\lambda_1,\lambda_3)$ for the associated Verma modules.

@@

Define the (super) character of an $E(3|6)$-module $M$ by the formula
\[
\ch \, M  \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
\]
As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
\[
M(V) = \Sym(\lie{g}_{<0}) \otimes V .
\]

Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.

@@

\subsection{Characters for degenerate modules of type $A$} \label{s:typeA}

There is a cohomological description of the irreducible modules of type $A$
\[
I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
\]
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\beqn\label{eqn:les1}
0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
\eeqn
%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]

\parsec[s:typeAunrefinedKR]
In this section we compute the {\em unrefined} character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
From the long exact sequence \eqref{eqn:les1} we have the following expression 
\[
\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} = \sum_{j \geq 0} \ch M(\lambda_1+j,0,\lambda_3+j;\frac23 \lambda_1 - \lambda_3 - \frac{j}{3}) .
\]

@@

There is a cohomological description of the irreducible modules of type B similar to the type A case above.
Let $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
We are only interested in the case $\lambda_1 = 0$ with $\lambda_3=0,1,\ldots$.  
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\begin{multline}\label{eqn:les1}
0 \leftarrow  I_B(0,\lambda_3) \leftarrow \\ \leftarrow M(0,0,\lambda_3;\lambda_3 + 2) \leftarrow  M(1,0,\lambda_3-1;\frac{11}{3} - \lambda_3)  \leftarrow \cdots \leftarrow M(\lambda_3, 0, 0;\frac23 \lambda_3 +2) \leftarrow \\
 \leftarrow M(\lambda_3+2, 0, 0; \frac23 \lambda_3 + \frac43) \leftarrow M(\lambda_3+3, 0, 1; \frac23 \lambda_3 + 2) \leftarrow \cdots .
\end{multline}
There are $\lambda_3+1$ terms in the second line above .
